\label{chap:introduction}


\section{Problem Statement}
\label{sec_problem}

Worldwide, colorectal cancer is one of the most common and deadly types of cancer. The third most comon cancer, accounting for aproximately 10\% of all cases, it is the second leading cause of cancer-related deaths. In 2022 alone, there were an estimated 1.9 million new cases and more than 900,000 deaths globally.
The symptons may include blood in the stool, changes in bowel habits,such ass diarreia or constipation, abdominal pain and unexplained weight loss. 

Besides being more common in individuals over 50 years old, there are a lot of factors that can increase the risk of developing the disease, such as low diet in fruits and vegetables, high consumption of red and processed meats, physical inactivity and obsesity. Alcohol consumption and smoking are also associated with an increased risk of developing colorectal cancer. In addition, there are some hereditary conditions that can increase the risk, such as familial adenomatous polyposis (FAP) and Lynch syndrome.
People with inflammatory bowel disease have higher chances of colon cancer, the worse the severity of the inflammation.

The most efficient way to treat, and even cure, a pacient diagnostic with colorectal cancer, is through early detection of the tumor. However, colonoscopy is a very invasive procedimment and not always can detect precisely the presence ou absence of the polyps, which are the main precursors of colorectal cancer. Futhermore, the acuracy of colonoscopy can be affected by third-party factors, such as the experience of the endoscopist and the quality of the bowel preparaiton. In addition, the lack of access to screening exams, especially in low-income regions, contributes to late diagnosis and worse prognosis for patients with colorectal cancer. Therefore, there is a need for more accurate and efficient methods for early detection of colorectal cancer, which can improve patient outcomes and reduce the burden of this disease on healthcare systems worldwide.



\section{Research Objectives}
\label{sec_goals}

This section complements the previous one. This section first to determine the scope of your work. It is a roadmap for your study. While the Problem Statement section explains what is wrong, the Research Objectives section state exactly what you plan to accomplish to solve the problem. Here you must to translate your broad research goals into actionable, measurable steps.

Example: "To develop an optimized classification system for ballistic wounds using Kolmogorov-Arnold Networks (KAN) and Transfer Learning." (general objective).

You can complete the general objective with specific (sub) objectives:

- To identify the primary visual features of different types of projectile trauma through a review of forensic literature.
- To implement a Transfer Learning framework for feature extraction from a specialized medical image dataset.
- To design a KAN-based architecture to classify wound types with high accuracy.
- To compare the computational performance of the KAN model against traditional architectures.

NOTICE: USE A DISSERTATIVE STYLE. DO NOT USE ITEMIZATIONS NOR LLM-STYLE SENTENCES.


\subsection{Research Hypothesis}
\label{sec_hypothesis}

A research hypothesis is essentially an "guess" or a tentative prediction about the outcome of your study. It is a declarative statement that you intend to test through your research. If the Research Objective is what you want to do, the Hypothesis is what you expect to find.

\section{Contributions}
\label{sec_contributions}

Section dedicated to make more explicit the contributions of your study. Included in the final of the Introduction chapter, it is is a explicit statement of the specific value, new knowledge, or technical advancement your work provides to the scientific community.

While the Objectives say what you did, the Contributions say why the field is better off now that you've done it. The Contribution is about originality of your work.


\section{Organization of This Document}
\label{sec_about}


This is the final roadmap of your Introduction. It provides a brief overview of how the rest of the TCC is organized.
