\label{chap:background}

The \gls{CL} is a procedure that allows doctors to examine the inner lining of the colon and rectum using a flexible tube with a lighted camera. The \gls{CLP} passes through the anus and rectum into the colon, providing images of the interior. Those images can be used to identify abnormalities such as polyps, which are growths that can develop into colorectal cancer if left untreated. 

However, the accuracy of colonoscopy can be affected by various factors, as discussed in Introduction \ref{chap:introduction}. Considering the importance of early detection of colorectal cancer, is undeniable that improving the accuracy of colonoscopy is a critical area of research. 

\section{Machine Learning and Computer Vision}
\label{sec_machine_learning}

\gls{AI} is a field of computer science dedicated to creating systems capable of performing tasks that typically require human intelligence. Examples of such tasks includes problem-solving, decision-making, and pattern recognition. \gls{ML} is an area of knowledge that focus on developing algorithms that allow computer system to learn from data and improve their performance without being explicit programmed. This mathematical relationship derived from the data is called model. Each revelant feature, or characteristc of data, must be represented numerically, so the model can \textit{learn}. 

The process to select which aspects of data to use in a machine learning process is called \gls{FE}, to improve performance and efficiency of machine learning algorithms. For a model to performe well, the quality of the its training data is essencial. Different architectures will have different approaches, as exposed in \ref{sec_models}.

Based on the nature and objective of it, a \gls{ML} can be categorized as one of the paradigms in the training process: \gls{SL}, unsupervised learning or reinforcement learning can be choosen after collect data. Besides that, a model can involve more than one approach in the end-to-end training process, in order to improve final performance.

\section{Data organization and Datasets}
\label{sec_dataset}
Not only in \gls{AI} context, data organization is more important than ever in the XXI century, considering that companies collect large amounts of data from various sources daily. Considering that, data must often be organized collections that make information accessible for analysis and application - called \gls{DS}.
However, there are more than one way of storing data, and different types of \gls{DS} store it in various ways. 

Structured \gls{DS} organize information in predefined structure, normally tables which each column is an attribute and each row an instance. In other hand, unstructured \gls{DS} contain information that does not fit in a rigid schema or cannot be resumed to a numerical or text value. Some examples of it can be images, videos, web-pages, documents or even applications. Futhermore, semistructured \gls{DS} don't follow rigid schemas, they incorporate defined syntax, such as json (JavaScript Object Notation), html (Hypertext Markup Language) or xml (Extensible Markup Language).

The type of task that can be solved or explored using \gls{ML} and \gls{AI} depends not only in the quality of data, but the type of the \gls{DS} that will train the model.

\section{Supervised Learning}
\label{sec_supervised_learning}
\gls{SL} goal is to make the model able to predit the \textit{correct} output for a given input. With that in mind, it applies to category problems, where the model outputs is compared to a \textit{ground truth}. Each instance of the \gls{DS} is labered with a discret value, such as numerical, representing which class or category it belongs to. According to the data and application context, a single instance can have multiple possible classes to be classified on.

While the train advances, the \textit{loss}, overall difference between the model’s output and the ground truth of training inputs, should drop, meaning the model is "learning" from the training process. If a model’s predictions are accurate, the loss is small. If its predictions are inaccurate, the loss is large. Different loss functions prioritize different types of error, so the choice of a loss function should reflect the nature of the data the model analyzes.

\section{Artificial Neural Networks and Deep Learning}
\label{sec_deep_learning}
For classification tasks is very common to use \gls{ANN} algorithms, a \gls{ML} model based on the biological neurons for \gls{SL}. In the human brain, neurons are connect to each other and communicate through electrical signals. Mathematically, this structure is represented by a fuction \(f(X)\) , that maps an input \(X = x1, x2, x3, ...\) to predict a output \(Y\).

\gls{ANN} is composed of three different parts, called \textit{layers}. Each one being composed of a group of \textit{neurons}. The first one is the \textit{input layer}, which receives raw data. The second consist of multiple layers, the \textit{hidden layer} consist of \textit{nodes} that transform inputs into new representation. They can be mathematically represented as a \textbf{linear transformations}, which the input features are multiplied by their associated weights and added bias to pass from one layer to the another. Finally, the \textit{output layer} applys to the output of the hidden layer a \textbf{nonlinear activation function} such as sigmoid, Relu, tanh, softmax and produce the final prediction.

Models with at least 4 layers are called \gls{DL} models. Not only can data be splitted into smaller pieces to make predictions, \gls{DL} often needs a massive amount of training data and computer perfomrance to reach optimal performance, considering the fact that some of more than millions or even a billion of parameters. The inclusion of multiple \textit{hidden layers} distinguishes a \gls{DL} from a "simple" \gls{ANN}, which allows the model to learn complex hierarchical features of data. The first ones identify broader paterns such as borders and deeper ones identify more granular patterns.

\subsection{Backpropagation and Gradient Descendent}
\label{sub_sec_backprop_gradi}
A \gls{DL} model updates its parameters in order to achieve greater precision in output predictions. To do so, is necessary that each of one of the millions, or even billions, parameters to be calculed separately, what can be have and tremendous computational cost considering the amount of neurons in a network. This process occurs after each \textbf{epoch} - a complete pass throught the train dataset, where the model process every sample, calculates loss and, finally, update it`s parameters.

Backward propagation erro, also referenced as \gls{BP}, is an algorithm to calculate how changes an individual weight or bias in  \gls{ANN} will affect the accuracy of predictions. By calculating the \textbf{gradient} - vector of partial derivatives of the \gls{LF} for each variable in every equation, it shows optimization algorithms - technics to adjust model parameters, each equations and parameters should be adjusted to reduce \gls{LF}.


\gls{GD} is an optimization algorithm  for minimizing a differentiable multivariate function. In \gls{SL}, it commonly works along side \gls{BP}, based on \textit{learning rate} - size of the steps necessary to reach minimum gradient. High ones means in highers steps, but may skip de converge point. However, small ones kill optimization efficiency.

For big amounts of data, dataset may be splitted into \textit{batchs} for efficiency. In this approach, an \textbf{epoch} consist of multiple iterations, which each process one batch. The number of iterations can be calculated by: \( iterationPerEpoch = totalSamples / batchSize\).

\subsection{Stochastic Gradient Descendent}
\label{sub_sec_stoch_grad}
Based on \gls{GD}, \gls{SGD} executes and updates parameters for each sample in dataset, one at a time inside an epoch. Easier to stay in memory than a \textit{batch} approach, it can reduce computational efficiency and generate noisy gradients.

\subsection{Mini-Batch Gradient Descendent}
\label{sub_sec_mini_batch_grad}
It combines \gls{SGD} with \textit{batch} approach, splitting dataset in small batches, called \textit{mini-batches} and updates model parameters in each of them.

\subsection{SGD with Momentum}
\label{sub_sec_sgd_momentum}
\gls{GDM} is an extension of \gls{GD} algorithm. Based on physics, where movement depends on current force and past velocity. The main goal of this approach is to smooth learning processo by adding past gradients, what leads to more stable convergence, which avoids \gls{BP} to skip the global minimum.

A new parameter called \textit{momentum factor} controls how mmuch of the past gradients are "remembered" in a update. Zero (0) means the optimizer will not consider past gradients and a value closes to one (1) will consider more past values.


\subsection{Adam}
\label{sub_sec_adam}


\subsection{Adamax}
\label{sub_sec_adamax}


\section{Models}
\label{sec_models}

\section{Evaluated Metrics}
\label{sec_metrics}