\label{chap:conclusions}

This work presents a comprehensive evaluation of multiple \gls{DL} architectures for \gls{CRC} classification. Several distinct approaches were implemented, including training models across various \glspl{DS}, validating their outputs using external \gls{CL} images from independent sources, and comparing model behaviors across multiple optimization techniques. Additionally, the performance of a hybrid quantum classical model was evaluated, which transforms raw medical images into feature rich representations to improve overall classification accuracy. Despite the variety of experimental scenarios tested, some of the utilized \glspl{DS}, such as \gls{LC25000} and \gls{CRC5000}, exhibited class imbalances and varied normalization states, which potentially influenced the empirical results detailed in Chapter~\ref{chap:results}.

The findings presented in Chapter \ref{chap:results} address several of the open questions raised in Chapter~\ref{chap:related} regarding existing research. Traditional \gls{DL} models can be effectively deployed for the automated detection and classification of colorectal anomalies with high prediction reliability. Architectures with fewer parameters, such as AlexNet, demonstrated promising performance when trained on the unnormalized variant of the \gls{NCTCRCHE100K} \gls{DS}, achieving accuracy and f1-score values exceeding ninety percent when paired with the \gls{SGD} and AdamMax optimizers.

The evaluated \gls{QNN} models demonstrated competitive robustness and promising outcomes, even when compared against structurally more complex \gls{CNN} and \gls{RNN} baselines. However, the lengthy training duration, particularly when processing higher resolution images, remains a critical area requiring improvement to facilitate more extensive, in depth studies. Furthermore, within environments like Google Colab, the utility of larger \glspl{DS} is significantly constrained by continuous runtime limitations. Continued advancements in Python simulation libraries for quantum hardware, alongside improved cloud computing infrastructure for \gls{QML}, are expected to expand the viability of these hybrid architectures across diverse domains, including oncology classification.

When evaluating the different \glspl{DS} proposed in Chapter \ref{chap:methodology}, the unnormalized version of the \gls{NCTCRCHE100K} image set, designated as NCT-CRC-HE-100K-NONORM, proved to be the most effective choice for training models intended to generalize well on external image sources. Although the models struggled to achieve optimal performance when predicting on the \gls{LC25000} \gls{DS}, the absence of the Macenko color normalization technique \cite{5193250} on that target set limits the definitive conclusiveness of these specific testing outcomes.

There are several potential areas of optimization that could be explored in future research. One immediate direction is the systematic implementation of the Macenko colorization technique \cite{5193250} on the \gls{LC25000} \gls{DS} to rigorously validate the generalization capability of models trained on \gls{NCTCRCHE100K}. Furthermore, training models directly on the \gls{CRC5000} \gls{DS} using data augmentation techniques offers a viable path to analyze its capability as a primary training set. Finally, architectural structural modifications to the proposed hybrid quantum classical framework \cite{quanvolution} provide significant opportunities to enhance model robustness. Ultimately, the broader societal impact of this research will be achieved by combining these classification frameworks with resource efficiency techniques, enabling their deployment on edge devices to democratize diagnostic technologies for the general population.