First and foremost, I would like to express my deepest gratitude to my parents for the love, care, and affection they have given me since the day I was born. I am profoundly grateful for everything—for every hug, every comforting embrace, every smile, every word of discipline, every lesson, and every conversation. My greatest source of pride is seeing so much of you reflected in the person I have become. From the bottom of my heart, I hope that one day I can make you feel as loved and valued as you have always made me feel throughout my life.

To my family, thank you for teaching me how to laugh and how to appreciate the beauty and colors of life. Without you, I would probably never have learned to smile in the face of adversity. Thank you for showing me that, even in life's most difficult moments, I will never be alone.

To my brother, Lucas, thank you for being far more than a brother. You were my very first friend, and having you in my life has brought me nothing but joy. You have no idea how important you are to me or how much your presence reminds me that life is truly worth living.

To my girlfriend, Carol, thank you for teaching me the true meaning of romantic love and how it encompasses every other form of love. Thank you for believing in me even when I could not believe in myself, for encouraging me during moments of discouragement, and, above all, for simply being who you are.

To my school friends, thank you for witnessing so many different versions of me and choosing to stay by my side through each one of them. The laughter and tears we have shared have shaped my life in countless ways. I wish each of you nothing but happiness and success.

To my university friends—my colleagues in the junior enterprise, the athletic association, and \textit{Não é Plágio}—thank you for showing me that every path holds unexpected joys and meaningful experiences. You were certainly mine.

To the forró community at the University of Brasília, thank you for the unforgettable moments and the friendships we built together. Above all, thank you for introducing me to a version of myself that I never knew existed.

To my dog, Rick, thank you for teaching me that love should be expressed every single day.

I would also like to express my sincere gratitude to Professor Pedro Garcia Freitas for his guidance, advice, and unwavering support throughout the development of this work, as well as for his dedication in ensuring its successful completion.

Finally, I would like to dedicate this work to the memory of Elenita Cruz Vaz, Lucilene de Jesus Pinto, Jaci Medeiros dos Santos, and Sebastião José dos Santos. There is not a single day that passes without me thinking of you. Please know that this will remain true for every day I have left. I love you.
